\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Fix heat plot

\subsection{Simulating the ``reddit effect''}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the ``reddit effect'' by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 64 Kb/s and performed benchmark tests that compared the performance of \zbf
against the HTTP content delivery latency under the throttled bandwidth conditions.

>>>>

\subsection{Simulating the ``reddit effect''}
Our tests involved programmatically opening browser windows and measuring load times.
Due to limitations of the number of browser windows that can be reasonably opened
and the memory overhead of Chrome, our browser testing environment of choice, we could
not reasonably open enough browser windows to exactly imitate millions of simultaneous
visitors to a site. Instead, we simulated the ``reddit effect'' by throttling the content delivery
bandwidth of the central server hosting the desired resource. We limited the content delivery
rate to 64 KB/s and performed benchmark tests that compared the performance of \zbf
against the HTTP content delivery latency under the throttled bandwidth conditions.
